Supplementary Information

### 2020-07-06 doc/manuscript/MEE_manuscript.Rmd

We analyzed previously collected tree-ring data from  # sites of the Forest Global Earth Observatory [ForestGEO; @anderson-teixeira_ctfs-forestgeo:_2015] representing a wide range of forest and tree types: tropical broadleaf deciduous and evergreen, temperate broadleaf deciuous and needleleaf evergreen, and boreal needleleaf evergreen (Table 1).
Trees were cored within or close to the large forest dynamics plots following a variety of sampling protocols designed to meet the varied objectives of the original studies [@vlam_temperature_2014; @maxwell_declining_2016; @sniderhan_growth_2016; @tumajer_increasing_2017; @alfaro-sanchez_growth_2017; @helcoski_growing_2019; MORE]. 
In using this variety of data sources, we encountered and solved a variety of challenges for analyzing existing tree-ring records with this approach.

>>>>

We analyzed previously collected tree-ring data from  # sites of the Forest Global Earth Observatory [ForestGEO; @anderson-teixeira_ctfs-forestgeo:_2015], plus one in New Mexico, representing a wide range of forest and tree types: tropical broadleaf deciduous and evergreen, temperate broadleaf deciuous and needleleaf evergreen, and boreal needleleaf evergreen (Table 1).
Trees were cored within or close to the large forest dynamics plots following a variety of sampling protocols designed to meet the varied objectives of the original studies [@vlam_temperature_2014; @maxwell_declining_2016; @sniderhan_growth_2016; @tumajer_increasing_2017; @alfaro-sanchez_growth_2017; @helcoski_growing_2019; MORE]. 
In using this variety of data sources, we encountered and solved a variety of challenges for analyzing existing tree-ring records with this approach.
